% !TEX program = xelatex

\documentclass[8pt]{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Shenghui Yang}

\basicInfo{
  \email{softwaredeveloper\_shy@outlook.com} \textperiodcentered\ 
  \phone{(+1) 412-608-8108} \textperiodcentered\
  \linkedin[Shenghui Yang]{https://www.linkedin.com/in/supermartinyang}}


\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{University of Pittsburgh}, Pittsburgh, PA}{2017 -- Present}
\textit{M.S.} in Information Science (IS), GPA 3.87/4.00, expected May. 2019
\datedsubsection{\textbf{East China University of Political Science and Law}, Shanghai, China}{2013 -- 2017}
\textit{B.S.} in Computer Science (CS), GPA 3.30/4.00

\section{\faUsers\ Experience}
\datedsubsection{\textbf{Clinical and Translational Science Institute} Pittsburgh, PA}{Jun. 2018 -- Present}
\job{Summer Intern}{Manager: Johne Rzodkiewicz}{Title: Full Stack Developer}
%Brief introduction: Full Stack Developer
\begin{itemize}
  \item Setup Event Registration System using ASP.NET and Database using MSSQL 
  \item Optimize network speed by using React.JS and simplify DB queries (Time Cosuming: 50\%)
  \item Build up CMS (content management system / Umbraco) for internal usage 
\end{itemize}

\datedsubsection{\textbf{CyRen Lab} Pittsburgh, PA}{Mar. 2018 -- Present}
\job{Research}{Manager: David Thaw}{Title: Research Assistant}
%Brief introduction: Member of Camouflage team
\begin{itemize}
  \item Deploy multiple systems on Xen and used Snort and pfSense as intrusion prevent and detect system to build a distributed honeynet
  \item Use methodology of machine learning to emulate human's activity towards a website to confuse hacker
\end{itemize}

\datedsubsection{\textbf{Zhong Ta Network Technology Co., Ltd} Shanghai, China}{Jun. 2016 -- Sept. 2016}
\job{Summer Intern}{Manager: Bingbing Wang}{Title: Web Developer}
%Brief introduction: Web Developer
\begin{itemize}
  \item Build up ThinkPHP framework for backend program and partitioning tables to improve searching speed
  \item Normalize tables to third normal form to prevent massive loading 
  \item Serve as departmental Linux Systems Administrator, develop shell scripts to improve working efficiency
\end{itemize}

% To
\section{\faUsers\ Projects}
\datedsubsection{\textbf{Tiny Web Server}}{Jun. 2016 -- Sept. 2016}
\role{C, Linux}{Individual Projects}
Brief introduction: A http Server coding in C, Improved it by adding concurrency feature
\begin{itemize}
  \item Fully support for serving multiple client with static and dynamic pages at the same time
  \item Allow people writing dynamic web page using C programming language
\end{itemize}

\datedsubsection{\textbf{Operating System Kernel}}{Sept. 2017 -- Nov. 2017}
\role{C, Assambly}{Individual Projects}
Brief introduction: Fully functional OS Kernel like Unix, based on knowledge learned in CS:APP
\begin{itemize}
  \item Deploy memory management (include DMA), file system (FAT), process management, and hardware drivers (e.g. keyboard)
  \item Optimize file system by using tree structure, making time complexity of searching file be O(log N) rather than O(N)
  \item Add security properties to file system and memory management in case of unauthorized access and bufferoverflow
\end{itemize}

\datedsubsection{\textbf{Cryptology Suite}}{Dec. 2017 -- Mar. 2018}
\role{Python}{Individual Projects}
Brief introduction: Based on Cryptology Algorithms, developed a suite for encryption and decryption
\begin{itemize}
  \item Provide DES, 3-DES, AES and PKI (RSA) cryptosystem within this suite, also with Message-Digest Algorithm (MD5, SHA-256)
  \item Optimize the program using table lookup instead of calculating (Time Consuming: 5\%) 
\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: C == Python > Java == C\# == shell > HTML == JavaScript ==  PHP
  \item Framework: Spring(Java), ThinkPHP(PHP), Express(Node.js), Django(Python), ASP.NET(C\#)
  \item Cloud: MapReduce, Big Table, Cassandra, Hadoop, Pig Latin, Spark
\end{itemize}

%\section{\faHeartO\ Honors and Awards}
%\datedline{\textit{\nth{1} Prize}, Award on xxx }{Jun. 2013}
%\datedline{Other awards}{2015}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
 % \item \homepage[http://your.blog.me]{http://your.blog.me}
  \item \github[https://github.com/supermartinyang]{https://github.com/supermartinyang}
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
